### 2008-03-01 trunk/SAiP/Module1/H3/doc/architecturaldesign.tex
Formatting of questions completed.

%%%
% Architectural Design
%%%
\subsection{Architectural Design -- Beer Web Store}
Consider the following main use case for a Beer Web Store for specialty
beers:
\begin{quote}
  The customer browses the beer catalogue for descriptions and
  reviews. The customer selects appropriate beers for purchase and
  these are added to his shopping basket. When the customer checks
  out, payment is validated through the payment service
\end{quote}
The main architectural drivers are considered to be performance and
availability. The software architect and stakeholders of the system
have based on this outlined the following two central Quality
Attribute Scenarios:
\begin{itemize}
  \item A customer makes a payment to the system in normal mode. The
  payment is processed within 10 seconds
  \item The payment service fails during normal operation. The system
  detects this. The administrator is notified and the system continues
  in degraded mode until the payment service is made available
\end{itemize}

Discuss:
\begin{itemize}
\item Give examples of performance tactics respectively availability
tactics that may be applied to the scenario. What are the consequences
of applying these tactics?
\item The software architect decides to use a layered architectural
style for the system. Discuss quality implications of this choice
\item Outline major elements of a possible component and connector
structure of the Beer Web Store system
\end{itemize}

>>>>

%%%
% Architectural Design
%%%
\section{Architectural Design -- Beer Web Store}
Consider the following main use case for a Beer Web Store for specialty
beers:
\begin{quote}
  The customer browses the beer catalogue for descriptions and
  reviews. The customer selects appropriate beers for purchase and
  these are added to his shopping basket. When the customer checks
  out, payment is validated through the payment service
\end{quote}
The main architectural drivers are considered to be performance and
availability. The software architect and stakeholders of the system
have based on this outlined the following two central Quality
Attribute Scenarios:
\begin{itemize}
  \item A customer makes a payment to the system in normal mode. The
  payment is processed within 10 seconds
  \item The payment service fails during normal operation. The system
  detects this. The administrator is notified and the system continues
  in degraded mode until the payment service is made available
\end{itemize}

\subsection{Architectural Design - Question 1}

\begin{question}
Give examples of performance tactics respectively availability
tactics that may be applied to the scenario. What are the consequences
of applying these tactics?
\end{question}

\fixme{Answer question 4.1}

\subsection{Architectural Design - Question 2}

\begin{question}
The software architect decides to use a layered architectural
style for the system. Discuss quality implications of this choice
\end{question}

\fixme{Answer question 4.2}

\subsection{Architectural Design - Question 3}

\begin{question}
Outline major elements of a possible component and connector
structure of the Beer Web Store system
\end{question}

\fixme{Answer question 4.3}
